$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Fixed typo

In this case we now consider realistic scenarios, where the
parameters that are not scanned over are set to values which keep the
associated states comfortably above their experimental limits.  So in
both the MSSM and E$_6$SSM, all other soft scalar masses are set
to $5$ TeV.  In order to avoid being in conflict with LEP
bounds on the chargino mass \cite{Kraan:2005vy} we exclude those points for
which the lightest chargino mass $m_{\tilde{\chi}^\pm_1} < 104$ GeV\footnote{In
fact this requirement has no impact on the bounds we find for the fine tuning
below. We found that, in the parameter space covered by our scans, including
points that violate the LEP bound does not lower the minimum fine tuning that
is obtained}.  We also impose several theoretical constraints on the points
included in the analysis.  In particular, we require a valid spectrum with no
tachyonic states to exclude points which would have an unrealistic minimum,
for example due to the appearance of charge or colour breaking (CCB) minima.
As a further requirement in the MSSM we exclude any points that do not satisfy
the well known CCB constraint \cite{Casas:1995pd},
\begin{equation} \label{eq:MSSMCCBconstraint}
A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
\end{equation}
or the unbounded from below (UFB) constraint,
\begin{equation} \label{eq:MSSMUFBconstraint}
m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
\end{equation}
We work in the third family approximation, taking the first and second
generation Yukawa couplings to be zero, and we also assume their associated
soft trilinears vanish.  Similarly we take $A_b = A_\tau = 0$ GeV.  The $U(1)$
gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix $M_3 = 2000$
GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is
held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.

>>>>

In this case we now consider realistic scenarios, where the
parameters that are not scanned over are set to values which keep the
associated states comfortably above their experimental limits.  So in
both the MSSM and E$_6$SSM, all other soft scalar masses are set
to $5$ TeV.  In order to avoid being in conflict with LEP
bounds on the chargino mass \cite{Kraan:2005vy} we exclude those points for
which the lightest chargino mass $m_{\tilde{\chi}^\pm_1} < 104$ GeV\footnote{In
fact this requirement has no impact on the bounds we find for the fine tuning
below. We found that, in the parameter space covered by our scans, including
points that violate the LEP bound does not lower the minimum fine tuning that
is obtained}.  We also impose several theoretical constraints on the points
included in the analysis.  In particular, we require a valid spectrum with no
tachyonic states to exclude points which would have an unrealistic minimum,
for example due to the appearance of charge or color breaking (CCB) minima.
As a further requirement in the MSSM we exclude any points that do not satisfy
the well known CCB constraint \cite{Casas:1995pd},
\begin{equation} \label{eq:MSSMCCBconstraint}
A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
\end{equation}
or the unbounded from below (UFB) constraint,
\begin{equation} \label{eq:MSSMUFBconstraint}
m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
\end{equation}
We work in the third family approximation, taking the first and second
generation Yukawa couplings to be zero, and we also assume their associated
soft trilinears vanish.  Similarly we take $A_b = A_\tau = 0$ GeV.  The $U(1)$
gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix $M_3 = 2000$
GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is
held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
